The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-06-07 Fsing/FThresholdsPaper/FThresholds.tex
added an example
Saving files before refresh
Small changes.

{\small
\setstretch{.67}
\begin{MyVerbatim}

@@

@@

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when
set to {\tt true} (the default value), {\tt fpt} first checks whether $f$ is a monomial, a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.

If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
When $f$ is a diagonal polynomial, a binomial, or a form in two variables, 
algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.  Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.

{\small
\setstretch{.67}
\begin{MyVerbatim}

i4 : fpt(x^3*y^4*z^5) -- a monomial

      1
o4 = -
      5

@@

i5 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial

      94
o5 = ---
     625

i6 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial

      997
o6 = ----
     6250

o6 : QQ

i7 : ZZ/5[x,y];

i8 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables

      5787
o8 = -----
     78125

o8 : QQ
\end{MyVerbatim}
}
\medspace

The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization. For this reason, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.

{\small
\setstretch{.67}
\begin{MyVerbatim}

i9 : L = {x, y, x + y, x + 3*y};

i10 : m = {2, 6, 9, 10};

i11 : fpt(L, m) == o8

o11 = true
\end{MyVerbatim}
}
\medspace

@@

As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned. Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to true, the precise interval will be printed.
{\small
\setstretch{.67}
\begin{MyVerbatim}

@@

\newpage
\section{Future Directions}
\label{sec.FutureDirections}

>>>>

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}

@@

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}
    i1 : R = ZZ/7[x,y];

    i2 : f = (x-1)^3 - (y-2)^2;

    i3 : nu(1, f)

    o3 = infinity

    o3 : InfiniteNumber

    i4 : nu(1, f, IsLocal => false)

    o4 = 5

    i5 : nu(1, x^3-y^2)

    o5 = 5

    o5 : QQ
\end{MyVerbatim}
}

@@

The {\tt fpt} function has the option {\tt UseSpecialAlgorithms}, which, when set to {\tt true} (its default value), tells {\tt fpt} to first check whether $f$ is a diagonal polynomial, a binomial, a form in two variables, or a product of factors in simple normal crossing, in that order.

%If $f$ is a monomial, then its $F$-pure threshold is simply the minimum of the reciprocal of the exponent of each variable in $f$.
When $f$ is a diagonal polynomial, a binomial, or a form in two variables, algorithms of Hern\'andez \cite{HernandezFInvariantsOfDiagonalHyp, HernandezFPureThresholdOfBinomial}, or Hern\'andez and Teixeira \cite{HernandezTeixeiraFThresholdFunctions},  are executed to compute the $F$-pure threshold.
Algorithms for computing $F$-pure thresholds of binomials also appear in \cite{ShibutaTakagiLCThresholds}, though they are only valid in certain special characteristics.

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}
i4 : fpt(x^17 + y^20 + z^24) -- a diagonal polynomial

      94
o4 = ---
     625

@@

i5 : fpt(x^2*y^6*z^10 + x^10*y^5*z^3) -- a binomial

      997
o5 = ----
     6250

o5 : QQ

i6 : ZZ/5[x,y];

i7 : fpt(x^2*y^6*(x + y)^9*(x + 3*y)^10) -- a form in two variables

      5787
o7 = -----
     78125

o7 : QQ
\end{MyVerbatim}
}
\medspace

The above noted algorithm for computing the $F$-pure threshold of a binary form $f$ requires factoring $f$ into linear forms, and {\tt fpt} can sometimes hang when attempting that factorization, when it happens in a Galois field of excessively large order.
This is a situation when the user will want to set the option \texttt{UseSpecialAlgorithms} to \texttt{false}.
However, when a factorization is already known, the user can pass to {\tt fpt} a list containing all the pairwise prime linear factors of $f$, and a list containing their respective multiplicities.

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}
i8 : fpt({x, y, x + y, x + 3*y}, {2, 6, 9, 10}) == oo

o8 = true
\end{MyVerbatim}
}
\medspace

@@

As seen in several examples above, when the exact answer is not found, a list containing the endpoints of an interval containing the $F$-pure threshold of $f$ is returned. Whether that interval is open, closed, or a mixed interval depends on the options passed; if the option {\tt Verbose} is set to true, the precise interval will be printed.

\medspace
{\small
\setstretch{.67}
\begin{MyVerbatim}

@@

%\newpage
\section{Future Directions}
\label{sec.FutureDirections}
